\chapter{Tension}

%\section{section title}

Joff Cassius, the Commissioner of the Eurasian pan-urban domain, sat behind the holodesk at his workplace with a distinctively grumpy facial expression when doors quietly slid open and three tall humanoid violet-skinned figures with elongated necks stepped in. The one in front wore large palladium medallion on a necklace, the other two were armed with heavy plasma rifles.

\say{May the infinite stars shine upon you, ambassador. What a pleasant surprise,} said Cassius, waving his hand towards the chair opposite his holodesk. Enwarian ambassador sat. His bodyguards remained by the door.

\say{Disagree. No pleasant. You must know already,} the short chopped sentences bounced and flew off ambassador throat. Their vocal tract was considerably different than that of humans, making it hard to say more than a few words at a time.

\say{I do, in fact,} replied Cassius. \say{And I assure you the perpetrator will soon be caught, tried and punished accordingly.}

\say{Doubt,} said ambassador.

\say{Please accept my condolences for the family of the victim. And, with all due respect, ambassador, your doubts are ungrounded. Never once the Earth authorities gave any reason to doubt the swiftness of its justice for the crimes committed in Earth jusrisdiction. I stress this especially: regardless of the race and origin}.

\say{Good,} ambassador stood up, waited a few seconds and added \say{My wish your words be truth}. And the three enwarians departed.

For some time commissioner sat in his chair motionless. Of course he knew, a brief came over the infocloud an hour ago. Just another drunken fight at the 'Galaxy Orifice' and someone kicked someone else a bit too hard. Just fifty years after the First Encounter, the interspecies cultural integration between mankind and enwarians went already too far. Bars that served both alcohol and blueish poisonous fluid that made enwarians go haywire and be like three sheets on the wind were just tips of the iceberg.

Interspecies murders were rare, though, but not unheard of, given several millions of enwarians having legal residence within Solar System. But as far as commissioner knew, none of the previous incidents of this kind warranted personal visit of the Enwarian ambassador to any of the Earth Commissioners.

Enwarians were masters of subtlety and allusion. The way they act, tone of their voices, their poses, gestures, ever slightest turn of their heads, all mattered no less than the words they say, which also conveyed many layers of meanings and hints.

This suggested more-than-usual importance of the victim, so it should be prudent to invest a personal attention into the case.

\say{Frank,} called commissioner peeking at the lower right corner of his holodesk. The area immediately lit green circle and reassuring voice of his assistant responded, \say{Yes, chief?}

\say{Find out who the victim was. And the suspect too, for that matter. Something is odd here.}

\say{Aye, chief.}

Joff pulled up the news aggregator interface over his holodesk and scrolled the titles for the recent hours. The local news were scarce on details as well. Scrolling further, Cassius slumbered.

Green circle rang so annoyingly Cassius regretted being born. \say{What?} he inquired.

\say{The victim is one Krax Kaudu The Hundred-Sixty-Second. There is not much on him in the infocloud. Just a regular guy, it seems}, reported Frank.

\say{But?} asked Cassius.

\say{What?} said Frank confusingly.

\say{There is always 'but' in a news like this, Frank}.

\say{Ermm\dots Yeah. But. You are not going to like this, chief, but the suspect is\dots It's Xander Pirius}.

Oh shit.

\say{Patrons saw them arguing while they were still inside. It escalated quickly and while security guards tried to see them out, Xander grabbed a paralyzer from one of guards and fired upon poor Krax. It was a human paralyzer, so the guy didn't have a chance.}

OH SHIT!

Xander Pirius was, as saying goes, the boy that shits gold. Having never worked a single day in his life, or even done anything to actually earn anything, he enjoyed every possible way of luxurious life available on Earth, systemwide and beyond. And of course, he is a biggest asshole, very handsome looking in his mid-twenties and walking cliche in general. The jewelry he casually wore was worth slightly more than the monthly budget of the entire Enceladean Union of Colonies.

This is what it means to be the only son and sole heir of industrial empire of Bogdan Pirius, leader of the Senate majority and, completely coincidentially, owner of every third industrial mine and mineral processing plant on Mars. Bogdan can buy you, sell you and buy you again but cheaper.

Joff Cassius mentally focused himself and said in calmest voice:

\say{Call Bogdan Pirius, private circuit, encrypted, urgent, official override.}

The holodesk blinked and a head of old man appeared on it. He had snow-white hair, piercing eyes and a cheekbone that looked almost like chiseled. He radiated immense superiority, authority and domination. His face was slightly turned away. He briefly glanced at Cassius and said firmly:

\say{No, I won't.}

\say{Mr. Pirius, this is a murder case. You must know the Statute gives me an executive authority to \dots } began Cassius, but Pirius interrupted:

\say{I don't give a flying fuck about your authority, moron. Those fucking turkeys can go fuck themselves. Xander stays with me.}

\say{Mr. Pirius, I would strongly advise against the direct confrontation with the police Marshals since this is an interspecies case and as such is under direct supervision of Sentient Species Affairs office,} lied Cassius since SSA was about the single thing that could potentially intimidate even an acting senator but they were unlikely aware of the incident yet.

\say{What part of 'I don't give a fuck' do you not understand, Joff? You don't have kids, so don't lecture me on how to take care of them.}

All right, thought Cassius, let's try this sideways.

\say{An ambassador Knoi paid me a visit just a few minutes ago. He was very concerned.}

Bogdan Pirius reached his holodesk and terminated the call, but at that mere moments before the screen went blank, Cassius could swear to have seen confusion, anger and fear on the Bogdan's face. What is going on?

\say{Call Eutimius Saintillon, private circuit, urgent} he said to his holodesk again. Holodesk blinked and displayed a man in a Marshals uniform but otherwise looking as what can be described as stereotypical non-remarkable office clerk. Even his smile gave an impression of being officially approved by some government regulation and followed to the minute detail.

\say{Good evening, Commissioner. How can I help you?} said Eutimius in a most clerkish voice.

\say{Head Marshal, I would like to hear of the progress on the investigation of 'Galaxy Orifice' murder case. And I will be extremely grateful if you shall convey the details not yet available to the public}, inquired Cassius.

\say{Commissioner, with all due respect, I must point out that such requests from the domain authority are out of protocol. Exerting administrative pressure on the police Marshals is forbidden.}, replied Eutimius monotonously.

\say{I am not exerting anything, Head Marshal. I am simply and humbly asking for any information that may prove vital to preserve good relationship with the Enwarian Continuity. I must also point out that witholding such information, should it be later proven that you did indeed possess it, especially in a case of interspecies murder, might cause Marshals office just a little bit of trouble with SSA}, said Joff in a menacing tone.

Saintillon stalled for a few seconds, considering the subtle threat and replied, \say{still we do not disclose the details of a pending investigation, Commissioner. All I can say is that qualifying the aforementioned incident as a muder is somewhat premature, if not outright speculative\dots }, but this time Commissioner had enough.

\say{Fuck it, Eutimius!} yelled Cassius, \say{for a Head Marshal you are too easily scared! I know it's Pirius bastard and I know Bogdan went mother hen full throttle, so stop playing games with me. Your people are on the scene. I only need to know who the hell was the victim and why was he so important that our old friend Knoi just casually stopped by my office.}

\say{Commissioner, your unwarranted emotional outburst do constitute what regulations define as administrative pressure, per se. I am sorry, but at this time I cannot comment, confirm or deny any claims or rumours pertaining the case in question. By the way, if ambassador Knoi visited you, why didn't you ask him to comment on the matter? After all, he is the first-hand source on it, is he not?}, asked Saintillon with apparent poisonous undertones in his voice.

Cassius deeply sighed and asked, \say{Bogdan called you, right? And scared your sorry and neck-deep-into-regulations ass to death, it seems. And you really staked your career against the possibility of a war.}

\say{Have a good day, Commissioner,} still calmly replied Saintillon and terminated the call. Unlike Pirius, his face didn't flinch even a bit.

There was another call to make, but before Joff could speak the call to his holodesk, the green circle rang with incoming call. He said \say{Accept} and holodesk displayed frontal view of a space suit in pilot's cradle, helmet with protective visor down. Background noise of the caller suggested a cruising spaceship. Deep female voice greeted Cassius, \say{May the infinite stars shine upon you, Commissioner}, and the visor slid up, partly revealing face of the voice's origin. Oh, those eyes, they incite the most pleasant memories, are they not? Somehow SSA already knew.

\say{And you, Aurora}, replied Cassius.

\say{You may be curious as to why I am calling you and not the Head Marshal}, said Aurora in a mellow voice.

\say{Not at all, Rory. It seems we both had a little chit-chat with Pirius and he told us both to fuck off, only I did not and Eutimius apparently did,} replied Cassius, \say{And I feel like I need your help.}

\say{Oh, this is sweet. How can I possibly help the almighty Commissioner of the Eurasian pan-urban domain? SSA is not exactly an instrument to influence the Senate}, replied Aurora, \say{but if you are serious about heeding my advice, think of contacting the PTMC. They crave every chance of poking a needle up Bogdan's ass.}

Cassius considered the idea. Post-Terranean Mining Corporation is the major competitor to the Pirius conglomerate. Slipping the hint of Bogdan harboring the murder suspect while directly confronting the police Marshals might give them good black PR opportunity. On the other hand, in order to work as intended, this must go public. But then Bogdan knows this too and is sure that Commissioner would seriously hesitate allowing such details to spread systemwide.

\say{Rory, who exactly is Krax Kaudu The Hundred-Sixty-Second? And why was I seeing ambassador Knoi earlier this evening?}

\say{We don't know. Enwarian Continuity isn't being too cooperative on the matter. But our inside sources tell of noticeable stirring up in their upper echelons. Take care, Jo.}

Well then. If Pirius is not going to play by the rules, neither will we.

\say{Call Declan Hagan, private circuit, urgent.} Holodesk blinked again and displayed a steaming surface of a bubbling pool. Cassius waited and in a few seconds a head emerged from underwater, a head of a man with a very annoyed facial expression.

\say{May the infinite stars\dots } began Cassius but Hagan interrupted him, \say{Shut it, Joff. I haven't been off-planet for months. Let me at least feel earthbound and have the luxury of seeing an actual horizon. Good fucking evening, Mr.Commissioner! Can you finally, for once, bring me some good news?.} Joff smiled and said \say{I can, in fact. Assuming you dispatch your least remarkable assistant to meet me by the Pirius place in half an hour.}

Hagan chuckled and replied \say{Thy will be done.}

Hagan guy's name was Clark. They both stood before the massive entrance gate to the Pirius palace. The gate was made of armored steel so thick it reminded Joff of the cargo bay door of a medium freighter spaceship. But then given the nature of Bogdan's business, it might indeed have been one.

Cassius held his ID against the intercom device on the gate and pressed 'Call'. This time Bogdan Pirius decided to not give Joff pleasure of seeing himself as intercom displayed 'voice only'.

\say{How are you still holding your position if you're clearly unable to learn your lesson on the first try?}, grumbled Bogdan.

\say{Let me talk to Xander, vis-a-vis. I'm not with the Marshals, this man is my assistant and we are unarmed,} started Cassius.

\say{Why would I do that?} inquired Bogdan.

\say{Because it is in the best interest of Xander}, replied Cassius, \say{I need to know exactly what happened to help SSA build a good defense strategy in case Knoi and his buddies decide to press the legal matters.}

Intercom went silent for a whole minute and then Bogdan's voice responded, \say{All right, I'll let you in. But hear this: no matter what Xander says he stays here as long as he wishes to.} The gate slid aside just enough for them to pass through and then slid back and sealed.

Xander Pirius sat on a simple wooden bench in the middle of what was perceived by the naked eye as a lush fruit garden. Unlike his father, he was seemingly much less confident. He glanced at Cassius and aksed angrily, \say{Did Knoi send you?} Joff gasped in surprise and replied, \say{Why do you ask this?} Xander looked down and anger in his voice withered.

\say{I didn't want to do it}, he began, \say{he made me do it.}

\say{He was such a nice guy, simple and quiet. We met just a week ago. Very reassuring and supportive, smart and honest. Unlike all those hypocritic imbeciles that surround me all the time. We've walked and talked for hours. It was like I had a true friend, for the first time in years. We were on the way to that pub when he suddenly stopped and confessed that he has the same feelings about me and asked if I wanted to achieve Mind Meld with him. He said no human before me was ever entitled to this privilege.}

\say{What is this Mind Meld?} inquired Joff. \say{I don't know, he was very vague on that,} Xander went on, \say{but I agreed empathically, I didn't care. I just wanted to be with him to continue this state of serenity that I felt when he was near me and he promised me that. Then he said that to achieve Mind Meld I have to kill him!}

\say{Interesting,} murmured Cassius, \say{please, go on.}

\say{He begged. He said if I didn't do it, he will suffer some horrible consequences, but didn't say what he meant. He said ambassador Knoi is after him and he didn't like that. We argued and almost fought. Then came the guards. I assume you know the rest. I hope he is happy now.}

\say{Thank you, Xander. We will start from here}, said Comissioner, then he and Clark left. But as soon as they stepped outside through the armored gate Joff noticed the glister of familiar palladium medallion. Violet skin is very hard to spot at night.

\say{I wish there was a proverb saying that to encounter the same Enwarian official twice a day brings luck}, said Joff.

\say{It may}, creaked ambassador Knoi, \say{how is your search for assailant?}.

\say{Underway}, politely replied Cassius, noticing how much easier Knoi speaks in long and grammatically correct sentences now.

Knoi glance was piercing and if only their facial muscles were able to convey emotions they would have conveyed anger and threat.

\say{Really,} said Knoi, \say{I believe you met him. Recently. Why is he not in custody?}

\say{Ambassador Knoi}, for the second time this night Commissioner had enough of this bullshit, \say{My understanding of the ambassadorial duties does not include interfering with the ongoing crime investigation, even if the victim is of your race. Simply speaking, by Earth laws, whether the suspect is in custody or not, is just not your business until the investigation is over. And even then you really should conduct any inquiries through SSA only, because my duties also do not involve active diplomatic relations behind their backs. The fact that I spoke with you earlier today and speaking with you again now is purely out of my good will, politeness and not any kind of obligation, per se. And by the way, Ambassador, I find your heated concern for the fate of the seemingly orinary Enwarian subject higly suspicious. Finally, would you care to explain what is Mind Meld? It may be crucial to the success of the investigation.}

Ambassador Knoi's eyes widened in surprise but he quickly calmed back. He waved towards his parked glider. Cassius instructed Clark to get back to Hagan immediately, they parted and he sat in the ambassador's vehicle. For a few moments Knoi was meddling with some kind of electronic device, so Cassius assumed it was a jammer against external eavesdropping. Then glider began moving down the street and away from Bogdan's palace and then finally Knoi decided to speak.

\say{You are bad dimplomat indeed. A half of insults you just said would warrant blood vengeance. But I am reasonable. This information is never meant for humans indeed. I too see our conversation as informal. Moreover, it never happened, right? So yes, Krax Kaudu The Hundred-Sixty-Second is not ordinary. A Mind Meld is a process of merging two or more minds of a sentient individuals. They merge so they share memories and life experiences. A very rough description of the process. Real Mind Meld more complicated. Only one individual survives, the one hosting the Meld. Rest die or merge the host bodily as well.}

\say{Do you know how Enwarian children are born?}, continued the Ambassador, \say{Parents merge their bodies into one progenitor host. They perform Mind Meld on each other. Out of progenitor host spawn younglings until its body mass is depleted. Long time ago. Before we went to space. Our children retained all parent's memories. But not anymore.}

Knoi went silent, Cassius patiently waited while they glided through the night streets.

\say{Enwarian High Seer is born in a similar way. The previous High Seer is included, of course. A special ritual is held. To pick up several individuals with whom to enrich the memories of the next High Seer. This is so High Seer knows the ways of people today. While retaining the wisdom of all previous High Seers. It is considered a high privilege to be included.}

\say{Oh, this makes sense now}, murmured Cassius, \say{I guess poor Krax was one of the 'included'? And what happens if one of the included die before the ... procedure?}

\say{If one dies of natural causes. Or in an accident. If the body survives. The Meld is still possible if hurried.}, replied Knoi, \say{but if killed. The killer must be included too.}

\say{What? But why?!}

\say{An Enwarian can do a partial Meld by himself. Uncontrollably. Under huge stress. Or while dying. So we must gather all pieces of mind of the included.}

Holy shit, thought Joff. If all of this is true, then split part of Krax Kaudu The Hundred-Sixty-Second mind may reside now in Xander brain and even very possibility of that, from the Enwarian point of view, qualifies him to be sacrificed in a ritual to produce their next spiritual leader.

Glider stopped and its doors swung open. Cassius stepped outside and said \say{Thank you for enlightening me, Ambassador. Rest assured, I will honestly try to help you with that situation.}

\say{You better do}, said Knoi, \say{also, read the Charter thoroughly}, and he left.

Joff raised his wrist-mounted mobile holodesk and said \say{Message to Aurora Galanis of SSA, private, urgent. Rory, I need you down here by tomorrow morning. Things are a bit more serious than we thought.}

Back at his residence, for a second Joff thought he had just shut his eyes when the holodesk rang. But the sun was well above the horizon already.

\say{Accept.} It was Declan Hagan, of course.

\say{Morning, Mr Commissioner! How is your investigation?}

\say{You woke me up, Declan. I will remember that.}

\say{All right, boy, down to business. What is it exactly you wanted to show me? Xander Pirius is a homosexual? Or xenosexual? Or both? No big news. You know, Enwarians do not even have any orifices suitable to fuck them. He killed someone? Ha-ha. That someone was Enwarian? Exotic but not workable either. So tell me why I should spend my precious time on it any more than I already spent?}

Cassius sighed deeply and said, \say{He killed an Enwarian who was very important for the process of \dots err\dots choosing their next High Seer. And Enwarians now demand blood vengeance or something like it.}

\say{Or else what? They launch a planetary assault on Bogdan's stronghold?}

Joff suddenly felt a jolt of anger. He said, \say{If you intended for this to be a joke, you've failed. They are damn serious about that. Not to mention the Enwarian battlecruiser on solar orbit somewhere between Earth and Mars, by Charter. We do not know for sure how important High Seers are for their society. But I bet they are very important. And I really do not like to theorize what they are capable of if their next High Seer cannot be produced because of us!}

\say{Us? Last time I checked, Xander Pirius was just one person. Thousands of people die every day systemwide for much less important and patriotic reasons.}

\say{Oh, yeah? Good luck convincing Bogdan Pirius that his heir is just an asset worth sacrificing to maintain galactic peace. Anyway, I gave you an exclusive information and I expect something in return. Make Pirius feel pressured and be nervous. I will connect SSA if needed. Thanks in advance, bye.}

