\chapter{Pressure}

One of the privileges the Commissioners were entitled to is having comfortable living quarters just few stories below their work offices and a private elevator between them. So in a few minutes Cassius, dresed and refreshed, sat in his chair behind the holodesk and eyeballed Head of the SSA Aurora Galanis while trying not to burst into laughter. Aurora was smiling back magnificiently. She was gorgeous and very athletic woman with long chestnut-colored braid and attentive grey eyes Cassius could only describe as 'engulfing'.

\say{All right, Rory,} Cassius broke the awkward stare contest with visible effort, \say{is there anything new you have learned since we spoke over the comms?}

\say{Actually, yes,} replied Aurora with a voice that send pleasant shivers down Joff's spine, \say{but it would be really helpful if you shared your insights first.}

Cassius sighed deeply and began, \say{Ugh... I guess there's no subtle way to put it. Long story short, Xander fell in love with this poor Krax but Krax demanded Xander to prove his feelings by murdering him in order to perform some kind of Enwarian voodoo magic by which their minds would merge and therefore they'd be together forever. Apparently Xander complied, hence the corpse, although no one knows if the trick had worked or not. Then it turned out that Enwarian High Seers are born using the similar procedure for which Krax was one of the few chosen. Enwarians now demand that we hand Xander over to them so they can complete the birth of the next High Seer, because they believe that Krax's mind may, just \textit{may} reside now inside Xander. Of course, Bogdan told everyone to fuck off and he was pretty convincing in doing so since now even Head Marshal refuses to acknowledge this wasn't accident but premeditated murder. I remember now it was Pirius who insisted at appointing Saintillon as Head Marshal, to everyone's surprise because we all knew how cowardly and unimaginative Eutimius was, not exactly a qualities of a good cop. See how that played well for Bogdan. What else? I also contacted Hagan and tipped him of some but not all relevant details but he wasn't much impressed. I doubt PTMC involvement will be of any use. Also I refreshed my memory about contents of the Charter and there is, indeed, explicit clause on the mutual alien extradition for individuals responsible for the threats to the basic functioning of the society. Well, that's about it}.

During all this speech Aurora sat with eyes widened and jaw dropped. Coming back to her senses, Aurora asked:

\say{Jo, please elaborate on 'it turned out'. Who or what is your source? This kind of knowledge doesn't come out of thin air. Our best xenobiologists don't know half as much as you just poured on me. How?}

\say{Rory, I am sorry but I can not betray the trust of my informants. I have my connections, why wouldn't I? They are rare to come by nowadays,} firmly replied Cassius.

\say{Your source was an Enwarian, that's for sure. No human knew this much before, or else it would have been common knowledge by now,} murmured Aurora, \say{anyway, my turn. Just about five hours ago we have detected powerful gravitational wave burst coming from approximately the orbit of Neptune. The wave signature matched that of hyperspace collapse point and its estimated power yield indicated the transition sphere at least hundred kilometers across. Four hours ago we received some imaging data as well of what looks like Enwarian convoy. A very strange convoy.}

\say{Oh crap. Don't tell me that's their punisher fleet,} whispered Cassius.

\say{Not quite. First, their military fleet never exits the hyper inside the system to minimize risk of an ambush. Second, there were no wave bursts immediately prior to this one, which indicates they flew in the hyper straight from the point of departure, i.e. in a big hurry. Third, the convoy appear to consist of a large freighter surrounded by double ellipsoid formation of at least hundred heavy destroyers. Finally, they don't use inertial transfer orbits, they go on a collision vectoring, directly towards Earth. Which means, they'll burn a holy tons of fuel to be here in about three days instead of six months and there will be no zero-gravity onboard either.}

Joff and Aurora exchanged glances at each other and went silent.

Cassius finally decided to break the silence to state the obvious: \say{It's the progenitor host for the new High Seer. Nothing else in the Galaxy warrants this overkill of hurry and protection.}

\say{Yep,} Aurora agreed, \say{and we have to extract Xander before that royal cavalcade arrives.}

\say{What for, exactly?} inquired Cassius, \say{Assuming we can do it, of course. No, Rory, I am dead serious. This kind of dilemma never happened to us before. On one hand we should dangle poor Xander on a fishook for Enwarians to, let's be straightforward about it, kill him. Oh, he is a criminal, all right, but just like that, no due process, no trial, no conviction? Because their belief system says so and they don't see him as an individual with rights anymore. On the other hand, we can say 'fuck the Charter, we are not going to surrender one of our own just because you want it'. And you know what makes me sick down my stomach is that popular opinion will surely favor the second option, and Bogdan knows this and will take gigantic leverage of it. There must be a way to neutralize him while keeping the situation legal.}

\say{There is one thing I am thinking of now}, said Aurora, \say{But the implications of that move are horrible. You can call the Earth Emergency Commission. Declare martial law. There is clear and present military threat from the Enwarians to the Earth domains. The military will crack open Pirius stronghold easily.}

\say{Oh heavens, Rory, what are you talking about? There are about ten million Enwarians systemwide and nine million of them on Earth. What will happen to them?}

\say{What is the alternative, Jo? We can deter the attack from this small fleet, even including that battlecruiser, but we do not really know for sure what military resources are at their disposal. No one can guarantee that in a week after our glorious victory a ten thousand battlecruisers will not pop up behind the Moon on a planetary bombardment trajectory and that will be the end.}

Heavy silence hung in the office.

\say{There has to be a non-violent solution}, whispered Cassius and continued in normal voice, \say{All right, I will issue an emergency call and we will see what can be done without too harsh measures. Meanwhile, send me the data on the convoy, Rory. I will have to make several visits shortly.} They stood up, exchanged hugs and parted their ways.

An hour later Joff Cassius stood before the entrance to the Enwarian embassy. He did not have to wait too long, the doors slid open and he was led by a guard to what by human standards was the conference room.

Knoi entered the room and sat on one of the cushions that served the role of a furniture.

\say{May the infinite stars shine upon you, Commissioner. What a pleasant surprise}, he said and Joff could have sworn Knoi meant to sound smirky.

\say{Are we shielded here, ambassador?}

\say{Quite so. What good news you brought upon me today?}

\say{Ambassador, you were forthright with me yesterday, probably more than I deserve. I came to return the favor, if only to avoid much more trouble than we are already in.}

\say{I am all attention.}

\say{You were right. I did see Xander to interview him, he is currently at Bogdans' place. I was allowed in on the condition that Xander stays there. According to him, Krax Kaudu The Hundred-Sixty-Second demanded that Xander kill him in order to perform what I now understand to be near-death Mind Meld as a proof of their mutual love. He also told me Krax mentioned you in their heated debate.}

Knoi sat silent and motionless.

\say{Ambassador, it seems that I actually came here for your help and I am pretty desperate. You do understand how politically powerful Bogdan Pirius is and how little we have leverage on him, legal or otherwise. And those leverages, if applied, have high chance of being, as saying goes, cure worse than illness. I also know of the convoy carrying the progenitor host for the next High Seer that set course to Earth. Now, before everything goes down the sinkhole, please, tell me what happens if Xander is not included in the Meld? And is there any other way to resolve this situation that you see and I missed?}

Knoi finally spoke, \say{Sometimes I regret not knowing how to swear. In your language.}

\say{Krax Kaudu The Hundred-Sixty-Second was a deep thinker\dots Erm. Philosopher? Yes. He publicly opposed the spiritual guidance. Of the High Seers. Disrespecting millenia-old traditions. Even calling for their line to be abandoned. Every generation has its dissenters,} continued Knoi, \say{The Inclusion Ritual is blind. It does not account for what the included think. Because the experience enrichment must be authentic. What an irony.}

Knoi paused for a few seconds and continued, \say{We spoke a few times. I threatened to repatriate him by force. He threatened to throw himself in the garbage incinerator. Either of these outcomes could have been acceptable, in theory. But it seems he decided to make our lives that much more complicated.}

Cassius was in a bit of a shock hearing this and asked, \say{Are you implying that he targeted Xander specifically, knowing in advance it would be near impossible for you to extract him for a ritual on a 'murder clause' despite the Charter? What an asshole.}

Knoi replied, \say{Yes. Knowing him I believe his plan was this convoluted. Concerning your second question. I do not know. The situation has no precedent. Murdering the included sometimes was used. To illegally influence the future High Seer's stance on certain matters. But then never before the culprit refused to give himself up, it defeats the whole purpose. And never before the culprit has been human with different motivation. On a wild guess, if no High Seer is produced soon, our people will start asking questions. Very unpleasant questions. The Continuity will have to yield the truth. And popular opinion may demand that the culprit is retrieved by force and order restored. Understand this, Commissioner. In an effort to avert war, I am at your side. I can even agree with late Krax on certain ideas. If it was up to me alone, I would have abandoned High Seers just to maintain peace. Nothing justifies war. But I am not alone. We are many and I bear responsibility, just as you do. I wish you good luck and all the wisdom.}

Ambassador Knoi stood up, signaling the audience is over and left the room.

Xander Pirius sat on the same wooden bench but this time environment projector created a scene of warm beach by the sea with waters so transparent you could 'see' the fish near the bottom. Seagulls screamed in the sky and palm trees slightly swayed in the wind.

The projection momentarily blinked allowing Bogdan Pirius to the scene. He was slowly walking towards Xander while carrying portable holodesk in one hand and a small black rectangular card in other. His son was staring at the projected skies.

\say{Xander,} called Bogdan, \say{if I didn't know any better I could have decided that you wanted my premature death.}

\say{Murder Coverup in Pirius family,} read Bogdan from his holodesk, \say{Drunken Enwarian VIP killed out of jealousy,} he paused for a few seconds and then continued, \say{What is the actual fuck, Xander? What is wrong with you?}

Not a muscle moved in Xander's body as he continued staring silently and indifferently at the projected sky.

\say{Xander? You hear me?}

His son finally broke the silence, looked at him and asked, \say{Dad, were you ever in love?}

\say{If I wasn't you wouldn't be sitting here like a beat dog and generally miserable, son. But before you start pouring your emotional crap over me again, let me cut it short: them turkeys ain't meant to be loved by us humans. God had made us and them this much different and placed this far apart for a reason.}

\say{No, it's not that,} whispered Xander.

Pirius-father raised the black card up and said, \say{The Earth Emergency Commision is called. Can you, please, at least explain why the fuck you are summoned there too?}

\say{I don't know,} replied Xander, \say{you let Cassius in, ask him. Seems like an excellent opportunity for that. I only told him exactly what I told you.}

\say{Uh-huh. Pack your shit, we're leaving.}

The deep underground facility under Peruvian Andes hosting Earth Defense Force command center was being used to convene Earth Emergency Commission for the third time.

Each of four Commissioners were present, as well as Head of the SSA, EDF Chief of General Staff and Pirius senior as leader of the Senate. Xander was visibly uncomfortable as if he somehow tried to minimize his presence.

Joff Cassius was standing on the dais and had just finished delivering the known facts to his peers in the room. The blurry image of Enwarian convoy loomed behind him on the wall screen.

Bogdan Pirius cleared his throat and said, \say{If I understood you correctly, that guy Krax-whatever-his-number could have jsut committed the suicide if he was so keen on not being included in the next High Seer, is that correct?}

\say{To our best knowledge, yes, Mr. Pirius. More so, he threatened to do just that under pressure from ambassador Knoi}, replied Joff.

\say{Amusing,} remarked Bogdan, \say{you do understand the implications of this, don't you? He knowingly manipulated my son in order to create a crisis that endangers the security of Earth. It is a conspiracy. And now}, he waved towards the screen, \say{it is a military threat. And I believe it should be dealt with accordingly.}

\say{No, Mr.Pirius,} said African Commissioner, \say{it doesn't work like that. You are not an automaton and the decision was yours. Very informed decision, from what we have just heard. In other words, it is you who created the crisis.}

\say{Shut up you damn monkey!} Pirius exploded, \say{I am fucking tired of hordes of imbeciles telling me how to care for my kids! Especially of those who have none! Isn't it easy to offer someone else's life for the greater good, eh?}

\say{Enough!}, shouted Aurora and stood, \say{Gentlemen. Calm down. Mr.Pirius, I am a mother of two. Hope this earns me some authority on the matter in your eyes. Mr.Adegoke, while your logic seems impeccable, one can hardly blame a parent for loving his children.}

A few silent seconds passed as both men calmed down and Aurora continued, \say{also, as a mother, I feel it a bit improper to treat and discuss Mr.Pirius Junior as an object. Why don't we hear him? Please, Xander.}

Xander stood and looked around the room. He wasn't used to any gatherings of people other than lush and intoxicating parties. Let alone to the company of people who govern the entire planet.

\say{I\dots I don't really know how to resolve this. During the time I spent with Krax Kaudu The Hundred-Sixty-Second I felt like my life have to change. The ways I lived before, the things I've done, things I own, it all feels kind of empty, soulless. Like I've never been really alive. And he\dots He taught me how to rethink it all. How to see my lifepath from different angle, in the context of the whole purpose of my existence.}

\say{I don't see how any of this esoteric shit is relevant,} said Bogdan.

\say{It is and very so,} replied Aurora, \say{Please, continue}.

\say{Krax once asked me what will be my legacy. In the sense of what will remain after I die. I began to tell him about Pirius conglomerate and how nearly half of the system depends on the resources produced by it and all of it bears my name, but he laughed and told me I didn't understand his question. He then explained that any resource is expendable and its origin is not inherent in the resource itself. It's only a label on the packaging, easily changed. And what will really be my legacy, what will really remain of me is the biography page in the infocloud and a few cross-references in the succession of conglomerate CEOs. He was right of course, I have never thought of it from that angle.}

\say{Oh boy, billions of people would have eagerly traded their miserable lives for what you are complaining about,} murmured Bogdan.

\say{Yes, father. It is because they, too, do not understand.}

\say{So, Xander, did he offer you any new insight on the meaning of life?} asked Commissioner Adegoke.

\say{In a way, he did,} replied Xander, \say{He remarked about how slow mankind evolve because we have to teach our children literally everything anew each generation and how much time it takes, while Enwarian children often retain almost complete combined memories of their parents through Mind Meld.}

\say{And then}, Xander hesitated, \say{one day he came to our usual meeting place visibly agitated, briefly explained his trouble with Knoi and then suddenly offered himself for me.}

American Commissioner smirked.

\say{No, not in that way,} Xander continued, \say{we were never physically close. He offered his mind, saying that with the experiences and knowledge of all his predecessor generations I could leave an imprint on mankind that can last for millenia.}

\say{You will surely do, whatever the outcome}, murmured EDF Chief of General Staff, making notes on his holodesk.

\say{Why did you have to kill him to do so?} asked Aurora, but Xander only shrugged.

\say{Probably because unlike ritualistic version, the individual Mind Meld only works in near-death situation and also to make sure it works in the intended direction and not from Xander to Krax,} theorised Cassius.

\say{Still the question remains,} said American Commissioner, \say{did it work? How do you know the Meld succeeded?}

\say{I don't know. I don't feel any different. Nothing like voices in my head, imprinted memories or suchlike,} replied Xander.

\say{Well then}, grumbled Bogdan, \say{why don't we just call the Ambassador Knoi and tell him Xander is clear and nobody of his violet buddies is inside his head and for him to fuck off finally?}

\say{It is not that easy, Mr.Pirius}, Aurora went on, \say{We don't know how and when the Meld actualizes in the brain of the host. That is assuming it even works on humans, albeit Knoi seem to be sure of that.}

\say{Gentlemen, lady, please}, intervened Joff, \say{all of this are technicalities. We need to reach a plan of actions. But first, let Xander finish.}

\say{Xander, do you now understand that you have been manipulated by Krax?} asked Cassius.

\say{Yes, I do. Sadly.}

\say{He used your emotional attachment to him to pursue his own domestic political agenda and to try to implement certain policy changes into Enwarian society that are perceived by Enwarians themselves as far too radical?}

\say{It seems so. This is exactly what he tried to teach me, don't you see? How to push society forward}, Xander's eyes were glistening.

\say{Oh, human history knows a lot of revolutionaries. Few of them fared well,} remarked EDF CoGS, again not looking at Xander.

Cassius did not really want to ask next question. The boy was obviously indoctrinated in Krax radical teachings. His gut feeling anticipated Xander's answer and all the shitstorm that will surely follow it. But he had to. Knowing that Bogdan Pirius will take revenge on him, on Enwarians, on Aurora and on pretty much everyone whom he will deem responsible. Joff stealthily reached under his table and found a row of buttons. Silently counting them, he found the correct one and pressed it.

\say{Xander}, began Cassius, \say{it is a hard question for us to ask, but I must. There is no good solution at hand. We, once again, must choose between two evils. Both, unfortunately, converge on you. Therefore it is up to you to decide.}

Cassius sighed deeply and continued, \say{You have two options. First, ignore Enwarian demands. The Earth will try to protect you but we don't really know what Enwarians are capable of militarily. There might be blood and gore. Second, accept Enwarian demands. The consequences are obvious, I guess.}

Bogan's eyes widened in shock, he yelled \say{What? No!} and tried to stand up from his chair but the chair suddenly sprang up a pair of metallic grips that captured his hands and held them. Another pair of grips captured his legs. His body fell back at the chair, still trying to rip off the grips but to no avail.

\say{What the fuck is this?}, Bogdan growled, \say{It's a treason! You can not detain an acting senator, you bitches! I'll make sure you serve your prison terms on the farthest uranium mines!}

\say{It is a martial law}, remarked American Commissioner, \say{approved by the Earth Commissioners, effective immediately within my domain. Or, to be more specific, within the premises of the EDF command center. We now can detain any citizen of any Earth domain who happen to be here with us, per Statute, see chapter 17, sections B through E.}

\say{I will make sure you suffer. All of you, fucking morons.}

\say{Mr. Pirius, please calm down}, Aurora picked up her most mellow voice, \say{the restraint is only temporary and is only to make sure Xander's choice is unimpeded and on his own free will. He is of age and perfectly capable of informed and conscious decisions. Xander, please.}

Xander looked at his father and said, \say{Dad, please. Have faith in me. If I don't do this right, we may all suffer much horribly than in uranium mines.}

He paused for a moment and then looked at Joff Cassius.

\say{Commissioner, you are good manipulator too. Consider this a compliment. When you put it like this, a choice between throwing mankind into war against Enwarians with uncertain outcome versus achieving what is effectively incorporeal immortality, the choice is a bit obvious, isn't it?}

\say{I didn't mean it like that}, murmured Joff.

\say{Neither shall I. But, you see, since Krax died I now believe in fate}, his voice gained energy and was ringing across the room, \say{I believe our encounter was not accidental. I was like an empty vessel on a useless path from nowhere to oblivion and he was too full of truths to hold them on his own.}

\say{Manipulation or not, he gave up his life so that I can have a chance to advance the humanity further up the path of civilization. That ought to be respected. We did not have enough time to talk this through, hence the initial confusion. But now I can see thanks to all your efforts. By letting myself into the new High Seer I am paving the way between human and Enwarian species unlike anything anyone had seen during all these years. The civilizational exchange on a levels previously thought impossible. I choose to accept Enwarian demands. Thank you.}

Xander returned to his chair, while Pirius Senior sat in his, immobilized, head down and tears were running down his face. For the second time in his life he felt that much desperate and helpless.
