\chapter{Incandescence}

They departed the conference room, leaving only Piriuses in it for their private moment before Xander's departure. In the hall adjacent to the room other Commissioners stood slightly to the side, while Cassius, Aurora and EDF CoGS stood by the door.

\say{Bogdan looks broken,} remarked Aurora, \say{it doesn't mean any good.}

\say{You bet}, commented EDF CoGS, \say{a man like him will take this deeply personally. He will exact revenge. And he will be right to do so, in a sense.}

Joff Cassius finally understood what had bothered him so much during Xander's speech.

\say{Listen,} he said, \say{something is off with Xander. All his friends and associates described him as generally unable to speak in long meaningful sentences without a pair of 'fucks' in between. But now just listen to him. 'Incorporeal immortality', 'civilizational exchange', that inspirational speech worth of Joan of Arc. What the hell with this newfound oratoric skills?}

\say{Krax is taking him over}, suggested Aurora.

An hour later Joff Cassius was flying his glider with Xander to the Enwarian embassy. Xander was silent almost all the way, but when they were on the final approach, he suddenly asked, \say{Commissioner, does it ever weigh you down? All these billions of people you are responsible for. Each having his own dreams, hopes, aspirations, failures, reasons and people to blame, reasons and people to continue for. I never thought of it this way.}

\say{Call me Joff. Yes, Xander, it does weigh me down. Every day. I busy myself with a routine to keep a grip on sanity.}

On a landing pad, before they disembarked the glider, Cassius activated his holodesk and called Frank:

\say{Frank, we need to look into reports of missing humans within the metropolitan area since the incident in the 'Orifice'. See if any of them stand out somehow as related to enwarians. Send it over as a text note, it is important.}

\say{Aye, chief.}

They were standing before the embassy door when it slid open and revealed ambassador Knoi behind it. He only momentarily glanced at Xander and Joff could have sworn by now he learned to recognize that type of emotional surprise and agitation.

\say{May the infinite stars shine upon you, ambassador,} greeted Cassius, \say{you seem to have developed a kind of habit of surprising me.}

\say{And you, Commissioner,} replied Knoi, \say{Come in, please.}

They proceeded to the same cushioned conference room, but unlike Joff and Xander, Knoi did not sit on the cushion and started to walk circles around the room.

\say{Speaking of surprises, Commissioner, I must admit you have outdone me by far,} began Knoi, \say{I thought I knew humans. Anyway, I am very impressed. And no less thankful. The Continuity will be eternally thankful for averting the crisis. To you personally and to mankind in general.}

Joff's wrist mounted holodesk sliently blinked and he quickly glanced on a small preview screen.

\say{Ambassador Knoi,} said Cassius, \say{Your thankfulness may come in handy just this moment. If I may, I would like to ask a very personal question to you and about you.}

Knoi stopped and looked at Joff. \say{Go on,} he said.

\say{It is a common knowledge that human language is hard to speak for enwarians. Not grammatically, of course, but phonetically. Simply speaking, we all got used to your people speaking common language in very short and chopped sentences.}

Ambassador Knoi turned his sight away from Joff.

\say{And yet}, continued Cassius, \say{you seem to have mastered this particular skill to a level beyond impressive and in a very, very short time. Literally a few days, if I remember the details of your visit to my office correctly. During any other time this would have remained a complete mystery for me. But I have just witnessed a very similar phenomenon occuring with this young man beside me, who, it is to be believed, already underwent some form of a Mind Meld.}

\say{I know what you are implying}, replied Knoi.

\say{I hope so. Otherwise your diplomatic immunity may seriously struggle with the charges of murder or unlawful incapacitation of a certain Jackson Ming, aged 36, secretary of Enwarian Continuity Trade Office, who mysteriously went missing that same evening we talked in your glider. Good pick though. He had no kids, no immediate family and if not for his girlfriend we may have not even noticed his disappearance.}

Knoi was silent. Anger began to boil inside Cassius.

\say{How? Why? What is the point? Didn't you say yourself that High Seer enrichment must be authentic and 'unadulterated'? We went above and beyond risking to embitter Bogdan Pirius against ourselves to hold our side of the promise in the Charter, while you just grabbed a random guy to pose as your prized 'culprit'? Not to mention it is a crime, ambassador. But beside that, I'm genuinely curious if the High Seer would have seen through this deception?}

\say{Not necessarily,} said Xander Pirius to much surprise of both Joff and Knoi, \say{there are certain tricks to the Meld especially when you hold one's mind within your own and High Seer lineage had no familiarity with human minds. It is risky but possible. I guess the Continuity Elders from that convoy contacted the Ambassador and demanded the culprit be produced at any cost. And not believing you were able to do it, Ambassador decided to cheat.}

\say{How do you...,} began Joff, but stopped, \say{Ah, yes. Good afternoon, Krax.}

Xander smiled.

\say{It is still me, Joff. But it feels much better knowing all this, really.}

Cassius stood and looking directly at Ambassador Knoi, said, chopping every word, \say{I will elevate this to the Earth Emergency Commission and will see your ambassadorial status be revoked and your residence on Earth or systemwide be denied. Consider yourself persona non grata, effective immediately.}

Not looking back at him, Knoi replied, \say{Don't bother. I will resign at once and will depart with the convoy.}

Cassius walked to the door opening and stepping through it, heard Knoi saying very quietly \say{I am sorry.}