\chapter{Serenity}

After the enwairan convoy had arrived to Earth orbit and Xander Pirius with former ambassador Knoi have boarded the gigantic freighter, a few weeks were as uneventful as they can possibly be. Except The Continuity had sent a new ambassador called Kmar, who, of course, wasn't nearly as much talkative or annoying as his predecessor. And except Bogdan Pirius have resigned his seat in the Senate, claiming he can not anymore serve the domains who failed to protect his son, and concentrated on his business empire. The rest was still uneventful.

One evening Joff sat behind the holodesk at his workplace and experienced a heavy stroke of deja-vu as three enwarians  stepped in, one bearing all too familiar palladium medallion on a necklace, the other two armed with plasma rifles.

\say{May the infinite stars shine upon you, ambassador Kmar. Please, have a seat} said Cassius, waving his hand towards the chair.

\say{And you,} creaked Kmar, \say{Good news!}

\say{I am listening,} replied Joff wishing the news be about the enwarian convoy finally departing back home. It can be visible with a naked eye in the night sky, even despite the massive light pollution of pan-urban domain and its presence unnerved Joff to no end.

\say{The High Seer. Visits Earth. Meets you.}

\say{Must be a great honor,} remarked Joff with a tone lacking any enthusiasm whatsoever.

\say{It is!}

Ambassador Kmar was not too observant of human emotions either. Probably for the best, concluded Cassius.

\say{Is there anything I need to know or prepare myself for?}

\say{No. Just be.}

\say{Thank you for invitation, ambassador. I gladly accept.}

And they left. Cassius, thanks to his introverted nature, did not particularly like official visits. Most of issues in his daily routine could easily be dealt with holodesk calls or instant messaging but this ancient remnant of official courtesy somehow remained through centuries.

And so next day, dressed more formally than usual and slightly nervous, Joff sat on the cushion in the all too familiar conference room in the Enwarian embassy, beind told to wait a couple of minutes.

The door slid open and Xander Pirius stepped in, dressed in traditional Enwarian gown.

\say{May the infinite stars shine upon you, Joff. Nice to see you again.}

Cassius froze in shock, his jaw dropped and he only managed to yield a squeak. He was seeing a ghost.

\say{With your permission, I'll take that as 'and you', Mr.Commissioner,} Xander was smiling and apparently enjoying the awkward situation he put Joff in.

\say{Have a drink,} said Xander and a floor tile right in front of Joff slid open and a glass levitated upwards for him to grab. Joff grabbed the glass without thinking, took a sip and asked:

\say{Who am I talking to?}

\say{Well, this is a bit too complex to explain in terms humans are familiar with,} began Xander, \say{For all intents and purposes I am the High Seer of the Enwarian Continuity. I am also Xander Pirius, at least in part. Whichever suits you, Joff.}

\say{How did that happen? Weren't you supposed to be dissolved in\dots?}

\say{I was. But we decided this will be a better outcome.}

\say{We?}

\say{The predecessors and the included. In no small part thanks to the fact that human body is stronger than that of enwarian. Also because Krax was very persuasive in his human studies. But not only that, of course.}

\say{Did you call your\dots Did you call Bogdan?}

\say{No, why would I?}

Joff had to remind himself that the entity before him looks human but, technically speaking, is not. And that Enwarian children never see their biological parents and thus have no chance of developing an attachment. Probably, this side of the original Xander was not developed much either.

\say{He thinks you are dead. To see you again alive and well will be a great news for him,} said Cassius.

\say{It is better that way, Joff. Believe me, I know him well. All and any of his possible reactions to this will only complicate his life even more.}

Joff had to admit this new Xander have a point. Bogdan might have a hard time accepting this entity, whose authority, power, intellect and knowledge easily outweigh his own, as his son. And the fact that he can no longer be the heir to his mining empire will be that feather that breaks the back.

\say{I see you surrendered your human side entirely, Xander. I cannot say I like it. I understand your logic though. Pragmatism, responsibility before your new people and all that. This kind of power depersonalize people all too much, and I am saying this from experience.}

\say{Occupational hazard,} commented Xander.

\say{Yes, but\dots Can I just ask you for a favor?}

\say{It depends. Try.}

\say{Bogdan has quite a vengeful reputation. Although he publicly blames the government for what happened to you, we know he is not beyond personal retribution. He is unlikely to do physical harm though, but you know, a pair of little PR stunts can easily destroy one's life and career nowadays.}

\say{All right,} agreed Xander, \say{I will let him know, but only that. Whatever happens because of it will be your responsibility.}

Cassius sighed.

\say{It is, Xander. It always is.}